CognatePriming_EyetrackingR

### 2021-05-21 Rmd/CP_eyetrackingR.Rmd
Added analysis section
Code for analysing model fit (growth curve) and bonferroni tests for specific comparisons of interest

# load packages
library("Matrix")
library("eyetrackingR")
library("tidyverse")
library("lme4")
library("ggplot2")

@@

@@

# Plot monolingual data with model fit curve
model_time_sequence_plot_mono_21 <- lmer(Prop ~ trial_type*(ot1 + ot2 + ot3) + 
                                               (1 | participant), 
                                             data = response_time_mono_21, REML = FALSE)

plot(response_time_mono_21, predictor_column = "trial_type", dv = "Prop", model = model_time_sequence_plot_mono_21) +
  theme_light() +
  xlab("Time from target & distractor image onset (s)") +
  ylab("Proportion of time looking at target") +
  ylim(c(0:1))

@@

@@

>>>>

# load packages
library("Matrix")
library("eyetrackingR")
library("tidyverse")
library("lme4")
library("ggplot2")
library("multcomp") # bonferroni

@@

############ 21 months ##################

@@

############ 25 months ##################

@@

############ 30 months ##################

@@

```{r analysis, eval=TRUE, echo = FALSE}

# Plot 21 month monolingual data with model fit curve
model_time_sequence_mono_21 <- lmer(Prop ~ trial_type*(ot1 + ot2 + ot3) + 
                                               (1 | participant), 
                                             data = response_time_mono_21, REML = FALSE)

plot(response_time_mono_21, predictor_column = "trial_type", dv = "Prop", model = model_time_sequence_mono_21) +
  theme_light() +
  xlab("Time from target & distractor image onset (s)") +
  ylab("Proportion of time looking at target") +
  ylim(c(0:1))

summary(model_time_sequence_mono_21)

# Post-hoc tests - only analyse significant predictors / interactions
#library(multcomp)
# To construct matrix, refer to summary()
contrast.matrix = rbind(
  "CP-NP" = c(0,-1,0, 0,0,0, 0,0,0,0,0,0), # ConditionCognate Prime(REFERENCE) - ConditionNon-Cognate Prime (Is there a significant difference between CP and NP?)
  "NP-UN" = c(0,1,-1, 0,0,0, 0,0, 0,0, 0,0), # ConditionNon-Cognate Prime - ConditionUnrelated Prime (Is there a significant difference between NP and UN?)
  "CP-NP_OT1" = c(0,0,0, 0,0,0, -1,0, 0,0, 0,0), # ConditionCognate Prime(REFERENCE) - ConditionNon-Cognate Prime (OT1, linear)
  "NP-UN_OT1" = c(0,0,0, 0,0,0, -1,1, 0,0, 0,0) # ConditionNon-Cognate Prime - ConditionUnrelated Prime (OT1, linear)
)
comps <- glht(model_time_sequence_mono_21, contrast.matrix )
summary(comps, test= adjusted("bonferroni"))
